AFQ-Insight

### 2019-12-16 reports/manuscript/sections/methods.tex
Update reports/manuscript/sections/methods.tex
Co-Authored-By: Ariel Rokem <arokem@gmail.com>

\item Diffusion MRI data from a previous study of properties of
the white matter across the lifespan \cite{yeatman2014lifespan},
containing dMRI data from 76 subjects with ages 6-50. These data were
measured in a GE Discovery 750 3T MRI scanner at the Stanford Center
for Cognitive and Neurobiological Imaging. The Stanford University
IRB approved the procedures of this study. Informed consent was
obtained from each adult participant, and assent for participation
was provided by parents/guardians for children. Voxel resolution was
\num{2x2x2}$\text{mm}^3$ with 96 non-colinear directions measured with a
$b=2000$ $\frac{\text{sec}}{\text{mm}^2}$ and 30 non-colinear directions
measured with a $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Data was
preprocessed to correct for subject motion and the diffusion tensor
model \cite{basser1994mr} was fit in every voxel, using a robust fit
\cite{chang2005restore}. These data were acquired using a dual spin echo
sequence, in which there is sufficient time for eddy currents to subside
between the application of the gradients and the image acquisition, so
no eddy current correction was appliced. We will refer to this dataset
as WH.

>>>>

\item Diffusion MRI data from a previous study of properties of
the white matter across the lifespan \cite{yeatman2014lifespan},
containing dMRI data from 76 subjects with ages 6-50. These data were
measured in a GE Discovery 750 3T MRI scanner at the Stanford Center
for Cognitive and Neurobiological Imaging. The Stanford University
IRB approved the procedures of this study. Informed consent was
obtained from each adult participant, and assent for participation
was provided by parents/guardians for children. Voxel resolution was
\num{2x2x2}$\text{mm}^3$ with 96 non-colinear directions measured with a
$b=2000$ $\frac{\text{sec}}{\text{mm}^2}$ and 30 non-colinear directions
measured with a $b=1000$ $\frac{\text{sec}}{\text{mm}^2}$. Data was
preprocessed to correct for subject motion and the diffusion tensor
model \cite{basser1994mr} was fit in every voxel, using a robust fit
\cite{chang2005restore}. These data were acquired using a dual spin echo
sequence, in which there is sufficient time for eddy currents to subside
between the application of the gradients and the image acquisition, so
no eddy current correction was applied. We will refer to this dataset
as WH.
